Quantum Semiprime Factorization: Leveraging Grover's Algorithm for Efficient Prime Decomposition

### 2025-03-31 LaTeX/paper.tex
Update paper, brief
Update paper

This paper describes the generalized use of Grover's algorithm as the
inverse of some function $F(x, y) = z$, with demonstrated applications
inverting the arithmetic functions addition and multiplication. The 
inverse of multiplication is a solution to prime factorization- a 
non-trivial problem with significant implications for cybersecurity
at a global scope.

@@

  Figure~\ref{fig:FIGURA2} shows an example of the oracle searching for the state $z=15$,
  or rather, $R_z=|001111\rangle$. To implement a circuit which can selectively target
  $z=15$, Toffoli gates (controlled-NOT) are applied on $R_z[0]$ and $R_z[1]$, 
  so that states where $R_z=|001111\rangle$ will temporarily be in
  state $R_z=|111111\rangle$, and the multi-controlled Toffoli gates\cite{multi_toffoli}
  will apply only for the desired states. These operations are then performed again,
  returning all but the target qubit (which has the Z-gate applied) to their original
  states.

>>>>

This paper describes the generalized use of Grover's algorithm as the
inverse of some function $F(x, y) = z$, with demonstrated applications
inverting the arithmetic functions addition and multiplication. Specifically,
our implementation can generate and simulate a circuit to find the distinct prime
factors of any given semiprime.

@@

  Figure~\ref{fig:FIGURA2} shows an example of the oracle searching for the state $z=15$,
  or rather, $R_z=|001111\rangle$. To implement a circuit which can selectively target
  $z=15$, Toffoli gates (controlled-NOT) are applied on $R_z[0]$ and $R_z[1]$, 
  so that states where $R_z=|001111\rangle$ will temporarily be in
  state $R_z=|111111\rangle$, and the multi-controlled Toffoli gates\cite{multi_toffoli}
  will apply a NOT operation to the target qubit only for the desired states (where $z=15$). 
  These operations are then performed again, returning all but the target qubit 
  (which has the Z-gate applied) to their original states.
